\documentclass{article}
\usepackage{amssymb, graphicx}
\graphicspath{ {images/} }

% Math-mode symbol & verbatim
\def\W#1#2{$#1{#2}$ &\tt\string#1\string{#2\string}}
\def\X#1{$#1$ &\tt\string#1}
\def\Y#1{$\big#1$ &\tt\string#1}
\def\Z#1{\tt\string#1}
 
\newcommand\tab[1][1cm]{\hspace*{#1}}

\renewcommand{\thesubsection}{\thesection.\alph{subsection}}

\begin{document}

\title{%
  Computer Aided Verification  \\
  \large Assignment 2 \\
    }

\author{1429527}

\maketitle

\section{For which of the two logics LTL and CTL (if any) are these legal (i.e., syntactically correct)
formulae? You can assume that a, b and c are atomic propositions.}

\begin{center}
\begin{tabular}{ c c c  } 
 
 (a) & $\Diamond$$\Box$$\Diamond$b & LTL \\ 
 \\
 (b) & $\exists$(c$\bigcup$$\forall$$\bigcirc$a) & CTL\\ 
 \\
 (c) & b $\land$ $\Box$ (a $\rightarrow$ $\bigcirc$ $\neg$ c) & Neither \\ 
 \\
 (d) & $\neg$ (( $\Box$$\Box$a) $\bigcup$ $\bigcirc$ (b $\land$ c)) & LTL\\ 
 \\
 (e) & $\exists$$\Box$$\Diamond$a & Neither\\ 
 \\
\end{tabular}
\end{center} 

\section{For each LTL formula, state whether the LTS satisfies it and, for each CTL formula, give the set
of states of the LTS that satisfy it.}

\begin{center}
\begin{tabular}{ c c c  } 
 
 (a) & c $\land$ $\bigcirc$ b $\land$ $\Diamond$ a & the LTS satisfies a \\ 
 \\
 (b) & $\forall$ $\bigcirc$ a $\land$ $\exists$ $\Diamond$ c & {$S_3$,$S_4$,$S_6$} \\ 
 \\
 (c) & $\exists$$\Diamond$ ($\exists$$\bigcirc$ (a $\land$ b) $\land$ $\exists$$\bigcirc$ ($\neg$a $\land$ $\neg$b))   & $S_5$ \\ 
 \\
 (d) & $\Box$$\Diamond$ (a $\land$ $\neg$c) & the LTS satisfies d \\ 
 \\
 (e) & $\Box$$\Diamond$ (b $\lor$ c) & the LTS does not satisfy e \\ 
 \\
\end{tabular}
\end{center} 


\section{Translate the following informally described properties into the specified temporal logic, explaining the meaning of any atomic propositions that you use.}

\subsection{“servers 1 and 2 are never both down simultaneously” (in CTL)}

$S_1$ = Server one is down
\smallbreak
$S_2$ = Server 2 is down
\smallbreak

$\neg$$\exists$$\Diamond$($S_1$ $\land$ $S_2$)

\subsection{“the robot eventually reaches room A and never passes through corridor B or C whilst
doing so” (in LTL)}

A = In room A
\smallbreak
B = In corridor B
\smallbreak
C = In corridor C
\smallbreak

$\neg$(B $\lor$ C) $\bigcup$ A

\subsection{“program location l 7 is visited infinitely often and program locations l 2 and l 3 are visited
only finitely often” (in LTL)}

$l_7$ = at program location $l_7$
\smallbreak
$l_2$ = at program location $l_2$
\smallbreak
$l_3$ = at program location $l_3$
\smallbreak

($\Box$$\Diamond$ $l_7$) $\land$ ($\neg$($\Box$$\Diamond$ ($l_2$ $\lor$ $l_3$))

\section{Using these (where needed), either prove or disprove each of the following proposed LTL equivalences. You can assume that a, b and c are atomic propositions.}

\subsection{$\neg$ ($\Box$$\Diamond$ a $\rightarrow$ $\Diamond$$\Box$b) $\equiv$  $\Box$$\Diamond$ a $\land$ $\Box$$\Diamond$$\neg$b }

$\neg$ ($\Box$$\Diamond$ a $\rightarrow$ $\Diamond$$\Box$b) 
\smallbreak

$\neg$ ($\neg$$\Box$$\Diamond$ a $\lor$ $\Diamond$$\Box$b) \hfill implication eq
\smallbreak

$\neg$ ($\neg$$\Box$$\Diamond$ a $\lor$ $\Diamond$$\neg$$\Diamond$$\neg$b) \hfill box eq
\smallbreak

$\Box$$\Diamond$ a $\land$ $\neg$$\Diamond$$\neg$$\Diamond$$\neg$b \hfill DeMorgan's Law
\smallbreak

$\Box$$\Diamond$ a $\land$ $\Box$$\Diamond$$\neg$b \hfill Box eq

\subsection{$\Box$ (b $\land$ c) $\rightarrow$ $\Diamond$ a $\equiv$ $\neg$ ($\Box$ (b $\land$ c) $\land$ $\Box$ a) }

The trace of only a e.g. {a, a, a, ...} satisfies the left side of the equality but not the right. A trace exists which satisfies one side but not the other, therefore they are not equivalent.    










\end{document}


